Proposition of a New Experiment to Better Understand the Relation Between Typicality and Prototypes

### 2022-05-13 paper.tex
Almost done ML part of Feature Extraction

			A more sophisticated technique than the ones listed before is shape analysis. Deformable shape analysis, in particular, can be useful to extract features from an image.\\
			In 2005, Felzenszwalb wrote a paper that focuses on representation and detection of deformable shapes~\cite{5}. For the goal of the experiment proposed here, some deformable shape 
			detection techniques can be useful. \\
			The technique proposed strongly relies on the trinagulated polygon representation. This type of representation lets approximate every 2D shape without holes using a representation based on triangles. 
			%The resulting approximation is as precise as the user decides, meaning that it's very flexible for the representation of shapes. 
			%In particular, in the paper the triangulation was done with a technique called constrained Delaunay triangulation (CDT), because of its tight relation with the medial axis transform. 
			The author also make use of the properties of chordal graphs and k-trees.\\
			The technique described in this paper falls under the category of deformable template matching. One of the components of the method is the energy function, a function that associates a cost with every 
			possible transformation. The objective is to find the transformation with the lowest possible cost. This component is very flexible, since depending on the formulation of the energy function the costs 
			can be tuned even for individual triangles. Moreover, it is also possible to integrate learning techniques to learn deformation parameters.
			Since the possible non-rigid transformations of a template are numerous, this kind of techniques usually requires an initialization near to the correct solution, 
			although this is not required for the algorithm presented in this paper. 
			For the implementation of the algorithm itself, a techniques called nonserial dynamic programming was the key factor. In fact, using the order of perfect elimination (property of the every triangulated 
			simple polygon), the algorithm computes the optimal position of every vertex with respect to the other vertices. Once the algorithm solves for the last vertex, it can 
			update all the others as in typical dynamic programming and obtain the optimal location for every vertex.\\
			The learning of the parameters can be seen as looking for the location with the highest. The matching problem is then fed to a statistical framework that computes the configuration minimizing the 
			energy cost, which corresponds to the best template match.

@@

		%\subsubsection{Madical imaging feature extraction techniques}

@@

@@

\bibitem{1} J. S. Owotogbe,T. S. Ibiyemi, and B. A. Adu, ``Edge Detection Techniques on Digital Images - A Review'', International Journal of Innovative Science and Research Technology, vol. 4, issue 11, Nov. 2019
\bibitem{2} Gaurav Kumar, Pradeep Kumar Bhatia, ``A Detailed Review of Feature Extraction in Image Processing Systems'', FourthInternational Conference on Advanced Computing \& Communication Technologies, DOI \url{https://doi.org/10.1109/ACCT.2014.7}, 2014
\bibitem{3} Dong Ping Tian, ``A Review on Image Feature Extraction and Representation Techniques'', International Journal of Multimedia and Ubiquitous Engineering, vol.8, pp. 385-396, July 2013
\bibitem{4} Chiranji Lal Chowdhary, D.P.Acharjya, Segmentation and Feature Extraction in Medical Imaging: A Systematic Review, vol. 167, pp. 26-36, Sep. 2019, doi: \url{https://doi.org/10.1016/j.procs.2020.03.179}
\bibitem{5} Pedro F. Felzenszwalb, ``Representation and Detection of Deformable Shapes'', IEEE Transactions on Pattern Analysis and Machine Intelligence, vol. 27, no. 2, pp. 208-220, Feb. 2005, doi: \url{https://doi.org/10.1109/TPAMI.2005.35}

>>>>

			A more sophisticated technique than the ones listed before is shape analysis. Deformable shape analysis, in particular, can be useful to extract features from an image.\\
			In 2005, Felzenszwalb wrote a paper that focuses on representation and detection of deformable shapes~\cite{4}. For the goal of the experiment proposed here, some deformable shape 
			detection techniques can be useful. \\
			The technique proposed strongly relies on the trinagulated polygon representation. This type of representation lets approximate every 2D shape without holes using a representation based on triangles. 
			%The resulting approximation is as precise as the user decides, meaning that it's very flexible for the representation of shapes. 
			%In particular, in the paper the triangulation was done with a technique called constrained Delaunay triangulation (CDT), because of its tight relation with the medial axis transform. 
			The author also make use of the properties of chordal graphs and k-trees.\\
			The technique described in this paper falls under the category of deformable template matching. One of the components of the method is the energy function, a function that associates a cost with every 
			possible transformation. The objective is to find the transformation with the lowest possible cost. This component is very flexible, since depending on the formulation of the energy function the costs 
			can be tuned even for individual triangles. Moreover, it is also possible to integrate learning techniques to learn deformation parameters.
			Since the possible non-rigid transformations of a template are numerous, this kind of techniques usually requires an initialization near to the correct solution, 
			although this is not required for the algorithm presented in this paper. 
			For the implementation of the algorithm itself, a techniques called nonserial dynamic programming was the key factor. In fact, using the order of perfect elimination (property of the every triangulated 
			simple polygon), the algorithm computes the optimal position of every vertex with respect to the other vertices. Once the algorithm solves for the last vertex, it can 
			update all the others as in typical dynamic programming and obtain the optimal location for every vertex.\\
			The learning of the parameters can be seen as looking for the location with the highest. The matching problem is then fed to a statistical framework that computes the configuration minimizing the 
			energy cost, which corresponds to the best template match.

@@

			After the classic techniques, machine learning began to be involved in feature extraction. In particular there are some papers that explain the results achieved with machine learning.\\
			In 2019, Halimi et al. wrote a paper about a feature extraction technique that they implemented using unsupervised deep learning~\cite{5}. Although this paper examines the techniques for 
			3D shapes, it's very likely that it can be adapted to extract 2D features from images.\\
			The background of this experiments is formed of some concepts that are not immediate. One of the concepts used as background is the minimum distortion correspondence. The other are, for example, 
			descriptor learning, functional maps and deep functional maps. These concepts serve as a base for all the work done later. \\
			In particular, the authors focus on unsupervised deep functional maps. The authors state that the main contribution of their paper is that they introduce a technique with which they can 
			avoid annotating a lot of data before training a model. After reducing the number of vertices to a number between 5000 and 7000, the authors used a deep functional map network. The inputs are 
			fed to two redisual neural networks, which compute a dense descriptor fields. These descriptors, are the inputs to the functional map layer. Lastly, as post processing, a point-wise map recovery was 
			applied and, after that, the shape was upscaled to the original resolution.

			\noindent In 2019, there is another paper, written by Varshni et al. that proposes another method~\cite{6}. This paper has the objective to classify images suing CNNs to understand if a patient 
			has pneumonia or not. After the preprocessing, in which the authors just resized the images, there is the feature extraction process. For this step, the authors used different pretrained models.
			In this paper's results it's reported that the best model architecture is DenseNet-169. This kind of neural netowrk, called Dense Nets, overcomes the problem of gradient vanishing. The model used in 
			particular for the work of this paper had 4 dense blocks and 3 transition layers. Then there is a classification layer.

			\noindent In 2019, Guamei et al. wrote a paper about hybrid feature extraction methods to classify brain tumors. The process described in the paper is divided into three points. The 
			first one is preprocessing, the second is feature extraction and the third is brain tumor classification. The first step is just to rescale the values to the range $[0,\ 1]$. The feature extractor 
			used is the GIST descriptor. The GIST is then combined with a Gabor filter and produces a total of $mxnx4x4$ GIST feature vectors. There is a variant of the GIST descriptor, the 
			PCA-NGIST is a PCA-based normalized GIST feature extraction method. The NGIST is a normalized version of the GIST descriptor, that uses the L2 norm to make the GIST invariant to illumination and shadowing. 
			After this step, the only thing left is the classification of the tumor, which was performed with a RELM classifier.

@@

		\subsubsection{Considerations about feature extraction}

		\subsection{Networks}

		\subsubsection{Convolutional Neural Network}

		\subsubsection{Siamese Neural Network}

@@

\bibitem{1} J. S. Owotogbe,T. S. Ibiyemi, and B. A. Adu, Edge Detection Techniques on Digital Images - A Review, International Journal of Innovative Science and Research Technology, vol. 4, issue 11, Nov. 2019
\bibitem{2} Gaurav Kumar, Pradeep Kumar Bhatia, A Detailed Review of Feature Extraction in Image Processing Systems, FourthInternational Conference on Advanced Computing \& Communication Technologies, DOI \url{https://doi.org/10.1109/ACCT.2014.7}, 2014
\bibitem{3} Dong Ping Tian, ``A Review on Image Feature Extraction and Representation Techniques'', International Journal of Multimedia and Ubiquitous Engineering, vol.8, pp. 385-396, July 2013
\bibitem{4} Pedro F. Felzenszwalb, ``Representation and Detection of Deformable Shapes'', IEEE Transactions on Pattern Analysis and Machine Intelligence, vol. 27, no. 2, pp. 208-220, Feb. 2005, doi: \url{https://doi.org/10.1109/TPAMI.2005.35} 
\bibitem{5} Halimi, Oshri and Litany, Or and Rodola, Emanuele and Bronstein, Alex M and Kimmel, Ron, Unsupervised learning of dense shape correspondence, Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition, pp. 4370-4379, 2019
\bibitem{6} Varshni, Dimpy and Thakral, Kartik and Agarwal, Lucky and Nijhawan, Rahul and Mittal, Ankush, Pneumonia detection using CNN based feature extraction, 2019 IEEE international conference on electrical, computer and communication technologies (ICECCT), pp. 1-7, 2019
\bibitem{7} Gumaei, Abdu and Hassan, Mohammad Mehedi and Hassan, Md Rafiul and Alelaiwi, Abdulhameed and Fortino, Giancarlo, A hybrid feature extraction method with regularized extreme learning machine for brain tumor classification, vol. 7, pp. 36266--36273, 2019
